Clustering and Parameter Estimation for the Popularity Adjusted Block Model

### 2020-07-14 summary.Rmd
cleaned up some typos and such

options(xtable.comment = FALSE, 
        xtable.table.placement = 'H')

import::from(magrittr, `%>%`)
import::from(foreach, foreach, `%do%`)
library(plot.matrix)
library(mclust)
library(ggplot2)

@@

set.seed(314159)

@@

```{r fig.cap = 'IQR clustering error using Algorithm 1 for sample sizes from 64 to 1024. Simulations were repeated 100 times for each sample size.', cache = TRUE}
results.df <- foreach(n = n.vec,.combine = dplyr::bind_rows) %do% {
  plyr::ldply(seq(iter), function(i) {
    Az <- draw.pabm.beta.2(n, a1, b1, a2, b2, alpha)
    A <- Az$A
    z <- Az$z
    clustering <- cluster.pabm(A, K)
    error <- mean(clustering == z)
    if (error > .5) error <- 1 - error
    dplyr::tibble(n = n, error = error) %>% 
      return()
  }, .parallel = TRUE) %>% 
    return()
}

@@

```{r}
n <- 64
z <- sample(c(1, 2), n, prob = c(alpha, 1 - alpha), replace = TRUE)
z <- sort(z)

@@

```{r q_trans, fig.cap = 'Pair plots of $ZQ$ where $Q$ was found by minimizing objective function (1). This embedding is equivalent to $XU$ up to 90-degree rotations and reflection along axes.'}
XU.prime <- transform.embedding(Z, z, runif(4, 0, 0))
pairs(XU.prime, col = z, asp = 1)
```

>>>>

options(xtable.comment = FALSE, 
        xtable.table.placement = 'H')
```

```{r}
import::from(magrittr, `%>%`)
import::from(foreach, foreach, `%do%`)
library(plot.matrix)
library(mclust)
library(ggplot2)

@@

@@

```{r fig.cap = 'IQR clustering error using Algorithm 1 for sample sizes from 64 to 1024. Simulations were repeated 100 times for each sample size.', cache = TRUE}
set.seed(314159)

results.df <- foreach(n = n.vec,.combine = dplyr::bind_rows) %do% {
  plyr::ldply(seq(iter), function(i) {
    Az <- draw.pabm.beta.2(n, a1, b1, a2, b2, alpha)
    A <- Az$A
    z <- Az$z
    clustering <- cluster.pabm(A, K)
    error <- mean(clustering == z)
    if (error > .5) error <- 1 - error
    dplyr::tibble(n = n, error = error) %>% 
      return()
  }, .parallel = TRUE) %>% 
    return()
}

@@

```{r}
set.seed(123456)

n <- 64
z <- sample(c(1, 2), n, prob = c(alpha, 1 - alpha), replace = TRUE)
z <- sort(z)

@@

```{r q_trans, fig.cap = 'Pair plots of $ZQ$ where $Q$ was found by minimizing objective function (1). This embedding is equivalent to $XU$ up to 90-degree rotations and reflection along axes.'}
XU.prime <- transform.embedding(Z, z, runif(4, -pi, pi))
pairs(XU.prime, col = z, asp = 1)
```
